### 2021-05-10 article/article.tex
update

\begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.49\textwidth}
         \includegraphics[width=1\textwidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
         \includegraphics[width=1\textwidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
   \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.05$
    to the standard interaction count}\label{fig:event_pulls} 
    %TODO: remake these with clearer titles and better labels, and reduce spacing between casc/tracks
    %also, consider normalizing color scheme to one single for both.
    %remove cos>0.
\end{figure}

@@

\begin{figure}[!tb]
   \begin{center}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_3D_NO.pdf}
         \caption{PINGU}\label{fig:PINGU_3D_NO}
      \end{subfigure}
      \hspace{1cm}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
         \caption{DeepCore}\label{fig:DC_3D_NO}
      \end{subfigure}
    \end{center}
    \caption{Minimization of the $\Delta \chi^2$ defined in Eq.~\ref{eq:chisq} after three years of data.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than the one shown in each panel are fixed to zero.}\label{fig:3D_NO}
 \end{figure}
%TODO:explain emt assymetry. dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
%TODO: ploit contour for ett-emt
 \begin{table}
   \begin{center}
   \begin{tabular}{lcc}
           \hline \hline \\
           Parameter & 90\% CL\hspace{1cm} & $3\sigma$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ & [-0.028, 0.044]\hspace{1cm} & \\
           $\emt$ & [-0.015, 0.0050]\hspace{1cm} & \\
           $\eem$ & [-0.068, 0.070]\hspace{1cm} & \\
           $\eet$ & [-0.072, 0.14]\hspace{1cm} & \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} PINGU } \\
           $\ett$ & [-0.036, -]\hspace{1cm} & \\
           $\emt$ & [-0.0076, 0.0085]\hspace{1cm} & \\
           $\eem$ & [-0.060, 0.055]\hspace{1cm} &  \\
           $\eet$ & [-0.065, 0.072]\hspace{1cm} &  \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} DeepCore + PINGU } \\
           $\ett$ & [-0.029, 0.0473]\hspace{1cm} & \\
           $\emt$ & [-0.0063, 0.0050]\hspace{1cm} & \\
           $\eem$ & [-0.046, 0.046] \hspace{1cm} & \\
           $\eet$ & [-0.057, 0.028] \hspace{1cm} &  \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
\end{table}

@@

\begin{figure}[t]
    \begin{center}
       \includegraphics[width=0.9\linewidth]{figures/joint_3D_NO.pdf}
    \end{center}
    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
    \label{fig:joint_3D}
 \end{figure}
%TODO: make 2x2. lines are too hin, colors are ugly. use spline smoothing.

>>>>

\begin{figure}[t]
   \begin{center}
         \includegraphics[width=0.9\textwidth]{figures/event_pulls.pdf}
   \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
    to the standard interaction count}\label{fig:event_pulls} 
\end{figure}

@@

\begin{figure}[!tb]
   \begin{center}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_3D_NO.pdf}
         \caption{PINGU}\label{fig:PINGU_3D_NO}
      \end{subfigure}
      \hspace{1cm}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
         \caption{DeepCore}\label{fig:DC_3D_NO}
      \end{subfigure}
    \end{center}
    \caption{Minimization of the $\Delta \chi^2$ defined in Eq.~\ref{eq:chisq} after three years of data.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than the one shown in each panel are fixed to zero.}\label{fig:3D_NO}
 \end{figure}
%TODO:explain emt assymetry. dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
%TODO: ploit contour for ett-emt
 \begin{table}
   \begin{center}
   \begin{tabular}{lcc}
           \hline \hline \\
           Parameter & 90\% CL & $3\sigma$  \\
           \hline \multicolumn{3}{c} {\hspace{1.5cm} DeepCore }  \\[0.1em]
           $\ett$ & [-0.029, 0.044]\hspace{1cm} & [-, -] \\
           $\emt$ & [-0.015, 0.005]\hspace{1cm} & [-, 0.015] \\
           $\eem$ & [-0.072, 0.075]\hspace{1cm} & [-0.132, 0.127]\\
           $\eet$ & [-0.074, 0.141]\hspace{1cm} & [-0.174, 0.2  ]\\\\
           \multicolumn{3}{c} {\hspace{1.5cm} PINGU } \\
           $\ett$ & [-0.033, -]\hspace{1cm} & [-0.048, -] \\
           $\emt$ & [-0.007, 0.007]\hspace{1cm} & [-0.011, 0.013] \\
           $\eem$ & [-0.062, 0.057]\hspace{1cm} & [-0.122, 0.103] \\
           $\eet$ & [-0.069, 0.077]\hspace{1cm} & [-0.121, 0.133] \\\\
           \multicolumn{3}{c} {\hspace{1.5cm} DeepCore + PINGU } \\
           $\ett$ & [-0.028, 0.043]\hspace{1cm} & [-0.043, -]\\
           $\emt$ & [-0.007, 0.005]\hspace{1cm} & [-0.011, 0.01] \\
           $\eem$ & [-0.048, 0.048] \hspace{1cm} & [-0.09, 0.085]\\
           $\eet$ & [-0.054, 0.072] \hspace{1cm} & [-0.101, 0.118] \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
\end{table}

@@

\begin{figure}[t]
    \begin{center}
       \includegraphics[width=0.9\linewidth]{figures/joint_3D_NO.pdf}
    \end{center}
    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
    \label{fig:joint_3D}
 \end{figure}
